### 2025-05-28 docs/article/Sections/results.tex
Sections 2,4,5: formatting
Section 3 & 5: update template engines table; Add HtmlFlow-Rx to Quarkus Results and change Sync to Blocking

The results in Figure~\ref{fig:presentations-webflux-jmeter} depict the
throughput (number of requests per second) for each template engine, with
concurrent users ranging from 1 to 128, from left to right. The benchmarks
include HtmlFlow using suspendable web templates (HtmlFlow-Susp), Jstachio
using Virtual Threads with the \texttt{Iterable} interface (Jstachio-Virtual),
and Thymeleaf using the reactive View Resolver driver (Thymeleaf-Rx).
\textit{Sync} and \textit{Virtual} represent the average throughput of the
blocking approaches (i.e., KotlinX, Rocker, Jstachio, Pebble, Freemarker,
Trimou, HtmlFlow, and Thymeleaf) when run in the context of a separate
coroutine dispatcher or Virtual Threads, respectively.

We show the HtmlFlow-Susp, Jstachio-Virtual, and Thymeleaf-Rx engines
separately to observe the performance of the non-blocking engines when using
the Suspending, Virtual Thread, and Reactive approaches. The \textit{Sync} and
\textit{Virtual} are aggregated due to the similar performance of different
engines when using those approaches.

\begin{figure}[h]
     \isPreprints{\centering}{}
     \includegraphics[width=0.8\textwidth]{./Graphs/presentations-webflux-jmeter.png}
     \caption{Presentation Benchmark Results in Spring WebFlux with JMeter}\label{fig:presentations-webflux-jmeter}
\end{figure}

@@

\begin{figure}[h]
     \isPreprints{\centering}{}
     \includegraphics[width=0.8\textwidth]{./Graphs/presentations-springmvc-jmeter.png}
     \caption{Presentation Benchmark Results in Spring MVC with JMeter}\label{fig:presentations-springmvc-jmeter}
\end{figure}

The results for the Spring MVC implementation, shown in
Figure~\ref{fig:presentations-springmvc-jmeter}, compare two approaches:
\textit{Sync}, which uses platform threads with \texttt{StreamingResponseBody},
and \textit{Virtual}, which uses Virtual Threads. Both approaches scale
effectively up to 128 concurrent users, with the Virtual Thread approach
achieving a slightly higher throughput of 9,000 requests per second. However,
these values are slightly lower than those observed in the Spring WebFlux
implementation.

\begin{figure}[h]
     \isPreprints{\centering}{}
     \includegraphics[width=0.8\textwidth]{./Graphs/presentations-quarkus-jmeter.png}
     \caption{Presentation Benchmark Results in Quarkus with JMeter}\label{fig:presentations-quarkus-jmeter}
\end{figure}

The results for the Quarkus implementation, shown in
Figure~\ref{fig:presentations-quarkus-jmeter} demonstrate that Quarkus handles
blocking approaches more effectively than Spring WebFlux, with the blocking
engines scaling up to 128 concurrent users and achieving 10,000 requests per
second. While the use of Virtual Threads results in a slightly higher
throughput, the difference is not significant, as both approaches deliver
similar performance.

@@

\begin{figure}[h]
     \isPreprints{\centering}{}
     \includegraphics[width=0.8\textwidth]{./Graphs/stocks-webflux-jmeter.png}
     \caption{Stocks Benchmark Results in Spring WebFlux with JMeter}\label{fig:stocks-webflux-jmeter}
\end{figure}

@@

\begin{figure}[h]
     \isPreprints{\centering}{}
     \includegraphics[width=0.8\textwidth]{./Graphs/stocks-springmvc-jmeter.png}
     \caption{Stocks Benchmark Results in Spring MVC with JMeter}\label{fig:stocks-springmvc-jmeter}
\end{figure}

@@

\begin{figure}[h]
     \isPreprints{\centering}{}
     \includegraphics[width=0.8\textwidth]{./Graphs/stocks-quarkus-jmeter.png}
     \caption{Stocks Benchmark Results in Quarkus with JMeter}\label{fig:stocks-quarkus-jmeter}
\end{figure}

The results depicted in Figure~\ref{fig:stocks-quarkus-jmeter} show that the
Quarkus implementation scales effectively up to 128 concurrent users, achieving
performance comparable to the Spring WebFlux implementation. The blocking
engines reach 6,000 requests per second. Again, there is no significant
difference between the Virtual Threads and platform threads approaches, with
both achieving similar results.

>>>>

The results in Figure~\ref{fig:presentations-webflux-jmeter} depict the
throughput (number of requests per second) for each template engine, with
concurrent users ranging from 1 to 128, from left to right. The benchmarks
include HtmlFlow using suspendable web templates (HtmlFlow-Susp), Jstachio
using Virtual Threads with the \texttt{Iterable} interface (Jstachio-Virtual),
and Thymeleaf using the reactive View Resolver driver (Thymeleaf-Rx).
\textit{Blocking} and \textit{Virtual} represent the average throughput of the
blocking approaches (i.e., KotlinX, Rocker, Jstachio, Pebble, Freemarker,
Trimou, HtmlFlow, and Thymeleaf) when run in the context of a separate
coroutine dispatcher or Virtual Threads, respectively.

We show the HtmlFlow-Susp, Jstachio-Virtual, and Thymeleaf-Rx engines
separately to observe the performance of the non-blocking engines when using
the Suspending, Virtual Thread, and Reactive approaches. The \textit{Blocking}
and \textit{Virtual} are aggregated due to the similar performance of different
engines when using those approaches.

\begin{figure}[h]
     \centering
     \includegraphics[width=0.8\textwidth]{./Graphs/presentations-webflux-jmeter.png}
     \caption{Presentation Benchmark Results in Spring WebFlux with JMeter}\label{fig:presentations-webflux-jmeter}
\end{figure}

@@

\begin{figure}[h]
     \centering
     \includegraphics[width=0.8\textwidth]{./Graphs/presentations-springmvc-jmeter.png}
     \caption{Presentation Benchmark Results in Spring MVC with JMeter}\label{fig:presentations-springmvc-jmeter}
\end{figure}

% The results for the Spring MVC implementation, shown in
% Figure~\ref{fig:presentations-springmvc-jmeter}, compare two approaches:
% \textit{Blocking}, which uses platform threads with \texttt{StreamingResponseBody},
% and \textit{Virtual}, which uses Virtual Threads. Both approaches scale
% effectively up to 128 concurrent users, with the Virtual Thread approach
% achieving a slightly higher throughput of 9,000 requests per second. However,
% these values are slightly lower than those observed in the Spring WebFlux
% implementation.

The results for the Spring MVC implementation, shown in
Figure~\ref{fig:presentations-springmvc-jmeter}, compare two synchronous
approaches: \textit{Blocking}, which uses platform threads with
\texttt{StreamingResponseBody}, and \textit{Virtual}, which uses Virtual
Threads. Note that for Spring MVC, which follows a thread-per-request
architecture, neither of the asynchronous approaches—\textbf{Reactive} nor
\textbf{Suspendable}—described in Section~5 are applicable. Regarding the
synchronous strategy, both \textit{Blocking} and \textit{Virtual} scale
effectively up to 128 concurrent users, with the Virtual Threads approach
achieving a slightly higher throughput of approximately 9,000 requests per
second. However, these values are slightly lower than those observed in the
Spring WebFlux implementation.

\begin{figure}[h]
     \centering
     \includegraphics[width=0.8\textwidth]{./Graphs/presentations-quarkus-jmeter.png}
     \caption{Presentation Benchmark Results in Quarkus with JMeter}\label{fig:presentations-quarkus-jmeter}
\end{figure}

The results for the Quarkus implementation, shown in
Figure~\ref{fig:presentations-quarkus-jmeter}, indicate that Quarkus handles
synchronous approaches more efficiently than Spring WebFlux. The blocking
engines scale up to 128 concurrent users, achieving up to 10,000 requests per
second. While the use of Virtual Threads results in a slightly higher
throughput, the difference is negligible, with both approaches delivering
comparable performance.

Additionally, \textit{HtmlFlow-Rx}, a reactive implementation of the HtmlFlow
template engine that utilizes Quarkus's reactive programming model, achieved
throughput similar to the \textit{Blocking} and \textit{Virtual}
approaches—approximately 10,000 requests per second. This demonstrates that
Quarkus's reactive programming model is effective for enabling PSSR\@. However,
there is no significant difference in performance between the reactive and
synchronous approaches, indicating that the reactive model does not provide a
substantial advantage over synchronous approaches in this context.

@@

\begin{figure}[h]
     \centering
     \includegraphics[width=0.8\textwidth]{./Graphs/stocks-webflux-jmeter.png}
     \caption{Stocks Benchmark Results in Spring WebFlux with JMeter}\label{fig:stocks-webflux-jmeter}
\end{figure}

@@

\begin{figure}[h]
     \centering
     \includegraphics[width=0.8\textwidth]{./Graphs/stocks-springmvc-jmeter.png}
     \caption{Stocks Benchmark Results in Spring MVC with JMeter}\label{fig:stocks-springmvc-jmeter}
\end{figure}

@@

\begin{figure}[h]
     \centering
     \includegraphics[width=0.8\textwidth]{./Graphs/stocks-quarkus-jmeter.png}
     \caption{Stocks Benchmark Results in Quarkus with JMeter}\label{fig:stocks-quarkus-jmeter}
\end{figure}

The results depicted in Figure~\ref{fig:stocks-quarkus-jmeter} show that the
Quarkus implementation scales effectively up to 128 concurrent users, achieving
performance comparable to the Spring WebFlux implementation. The blocking
engines reach approximately 5,500 requests per second, and once again, there is
no significant difference between the \textit{Blocking} and \textit{Virtual}
approaches, with both achieving similar results.

In addition to the blocking engines, the \textit{HtmlFlow-Rx} approach also
achieves a throughput of approximately 5,500 requests per second, matching the
performance of the \textit{Blocking} and \textit{Virtual} approaches. This
further demonstrates that there is no significant difference in performance
between the reactive and synchronous approaches in this context.
